Ice-shelf ocean boundary layer dynamics from large-eddy simulations

### 2021-07-01 main.tex

The simulation duration is $\sim$50 h, corresponding to $\sim$4 inertial periods of 13 h. By this point, the turbulent intensity as measured by the maximum vertical velocity fluctuation, is reasonably steady-state over one inertial period for the 1$^{\circ}$-slope simulations (Figure S1). The turbulent intensity for cases with slopes less than 1$^{\circ}$ continues to decline, as we discuss later. Many of the results presented are averaged over the last simulated inertial period and only the depths outside the sponge layer are shown.

@@

% Description of time evolution
Melt rates decline over the course of the simulations (Figure \ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs. This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations (Figure S1). We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
    \end{minipage}%
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
    \end{minipage}%
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
    \end{minipage}
    \caption{Time evolution of (a,c) melt rate and (b,d) friction velocity for (a,b) thermal driving simulations and (c,d) varying slope simulations. Y-axis limits differ between panels, with the black curve representing the same simulation in all panels.}
    \label{fig:timeseries}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}
    \caption{Depth profiles of simulated properties as they vary with thermal driving, averaged over the last inertial period. (a) temperature relative to far-field temperature, (b) salinity relative to far-field salinity, and (c) velocity components. For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).}
    \label{fig:dT_profiles}
    % change colorbar label to \theta_\infty
\end{figure}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_43h_tav13h_z_profile.png}    
    \end{minipage}
    \newline
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 11cm 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}
    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
    \caption{(a) Simulated turbulent kinetic energy for variable slope simulations averaged over the last inertial period and (b-d) turbulent kinetic energy production terms over the same period. (b) Shear production. (c) Buoyancy production. The total buoyancy production is shown with solid lines, vertical component dashed, and upslope component dotted. (d) TKE transport. Positive denotes production, negative destruction. Note that the x-axis scales differ between panels.}
    \label{fig:tke_budget}
    % Change x-axis label for buoyancy production terms
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 1cm 4cm 1cm},clip,width=\textwidth]{Figures/dslope2/pt_xz_y64_zmax42_t40.png}
    \end{minipage}%
    \begin{minipage}{0.55\textwidth}
        \includegraphics[trim={0 1cm 0 1cm},clip,width=\textwidth]{Figures/dT1/pt_xz_y64_zmax42_t40.png}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 1cm 4cm 1cm},clip,width=\textwidth]{Figures/dslope2/sa_xz_y64_zmax42_t40.png}
    \end{minipage}%
    \begin{minipage}{0.55\textwidth}
        \includegraphics[trim={0 1cm 0 1cm},clip,width=\textwidth]{Figures/dT1/sa_xz_y64_zmax42_t40.png}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
        \includegraphics[trim={0 0cm 1cm 0},clip,width=\textwidth]{Figures/dslope2/v_xy_z1_zmax1_t40.png}
    \end{minipage}%
    \begin{minipage}{0.45\textwidth}
        \includegraphics[trim={1cm 0cm 0cm 0},clip,width=\textwidth]{Figures/dT1/v_xy_z1_zmax1_t40.png}
    \end{minipage}%
    \begin{minipage}{0.05\textwidth}
    \hfill
    \end{minipage}
    \caption{Instantaneous flow structures observed at 40h in (a,c,e) 0.01$^{\circ}$ slope case and (b,d,f) 1$^{\circ}$ slope case. (a,b) Temperature in cross section mid-way through the y-axis. (c,d) Salinity in cross-section mid-way through the y-axis. (e,f) Cross-slope velocity fluctuations at 1 m below the ice-ocean interface. Note that the colorbar scale is smaller in (e) than (f).}
    % Add contours to a-d to show structures more clearly
    \label{fig:cross-section}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 3cm 0cm},clip,width=\textwidth]{Figures/dslope2/e_hovmoller.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/e_hovmoller.png}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 3cm 0cm},clip,width=\textwidth]{Figures/dslope2/vel_var_ratio_hovmoller.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/vel_var_ratio_hovmoller.png}
    \end{minipage}
    \caption{Example of turbulent intermittency as seen in (a,b) TKE and (c,d) vertical velocity variance. (a,c) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope. (b,d) An intermittent case: 0.45$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
    \label{fig:intermittency}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dT_tav12.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4.1cm 0 0cm},clip,width=\textwidth]{Figures/gammaT_dT_tav12_zlim2.png}
        \vspace{0.7cm}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 3.4cm 0 0cm},clip,width=\textwidth]{Figures/gamma_T__us__dslope_tav12_tlim52.png}
        \centering
        \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
    \end{minipage}
    \caption{(a) Melt rate vs. thermal driving. (b) Melt rate vs. slope. (c) Thermal exchange coefficient vs. far-field thermal driving for thermal driving simulations. Dashed line denotes the value recommended by \citeA{jenkins_observation_2010}. (d) Thermal exchange coefficient vs. friction velocity for sloped simulations. Note the difference in y-axis limits from (c). The 0.01$^{\circ}$ and 0.1$^{\circ}$ slope cases are overlapping.}
    \label{fig:melt_sensitivity}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_44h_tav12_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_slope_46h_tav12_z_profile.png}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13_dTscale_z_profile.png}
        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_slope_46h_tav13_slopescale_z_profile.png}
        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
    \end{minipage}
    \caption{Vertical profile of heat flux averaged over the last inertial period for (a,c) temperature cases and (b,d) slope cases. (a,b) are in physical units while (c,d) are scaled by the Ekman depth, far-field thermal driving, and slope. The black curve is represents the same simulation in all panels.} 
    %Consider replacing (d) with scaling by sin\alpha
    %Change scaled vertical axis limits to 0-40
    %Change all to centered on 43h and averaged 13h
    \label{fig:heatflux_profiles}
\end{figure}

@@

\begin{figure}[h!]
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_44h_tav12_z_profile.png}
        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_46h_tav12_z_profile.png}
        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
    \end{minipage}
    \caption{Momentum flux averaged over the last inertial period for (a) thermal driving cases and (b) slope cases. Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid). Positive flux denotes upward flux (i.e., drag) and }
    \label{fig:momflux_profiles}
    % change x-axis labels to \overline{u_i'w'}
\end{figure}

>>>>

The simulation duration is $\sim$50 h, corresponding to $\sim$4 inertial periods of 13 h. By this point, the time-mean kinetic energy of the flow has reached steady-state. However, the turbulent intensity for all cases continues to decline, with more pronounced TKE loss at lower slopes (Figure \ref{fig:timeseries}a,d). Many of the results presented are averaged over the last simulated inertial period and only the depths outside the sponge layer are shown.

@@

% Description of time evolution
Melt rates decline over the course of the simulations (Figure \ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs. This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations. We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/tke_cmp_dT_t.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
    \end{minipage}
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/tke_cmp_dslope_t.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
    \end{minipage}
    \caption{Time evolution of (a,d) domain-averaged turbulent kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations. The black curve representing the same simulation in all panels.}
    \label{fig:timeseries}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.33\textwidth}
        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}
    \caption{Depth profiles of simulated properties as they vary with thermal driving, averaged over the last inertial period. (a) temperature relative to far-field temperature, (b) salinity relative to far-field salinity, and (c) velocity components. For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).}
    \label{fig:dT_profiles}
    % change colorbar label to \theta_\infty
\end{figure}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_43h_tav13h_z_profile.png}    
    \end{minipage}
    \newline
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}
    \caption{(a) Simulated turbulent kinetic energy for variable slope simulations averaged over the last inertial period and (b-d) turbulent kinetic energy production terms over the same period. (b) Shear production. (c) Buoyancy production. The total buoyancy production is shown with solid lines, vertical component dashed, and upslope component dotted. (d) TKE transport. Positive denotes production, negative destruction. Note that the x-axis scales differ between panels.}
    \label{fig:tke_budget}
    % Change x-axis label for buoyancy production terms
\end{figure}

@@

\begin{figure}[]
    \centering
    \begin{minipage}{0.45\textwidth}
        \includegraphics[trim={1cm 0 3cm 0},clip,width=\textwidth]{Figures/pt_slope01_xz_y64_zmax42_t40.png}
    \end{minipage}%
    \begin{minipage}{0.55\textwidth}
        \includegraphics[trim={1.5cm 0 0.5cm 0},clip,width=\textwidth]{Figures/pt_slope1_xz_y64_zmax42_t40.png}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
        \includegraphics[trim={1cm 0 3cm 0}, clip, width=\textwidth]{Figures/sa_slope01_xz_y64_zmax42_t40.png}
    \end{minipage}%
    \begin{minipage}{0.55\textwidth}
        \includegraphics[trim={1.5cm 0 0.5cm 0}, clip, width=\textwidth]{Figures/sa_slope1_xz_y64_zmax42_t40.png}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
        \includegraphics[trim={1.5cm 0 3.4cm 0},clip,width=\textwidth]{Figures/v_slope01_xy_z1_zmax1_t40.png}
    \end{minipage}%
    \begin{minipage}{0.6\textwidth}
        \centering
        \includegraphics[trim={2cm 0 0.5cm 0},clip,width=\textwidth]{Figures/v_slope1_xy_z1_zmax1_t40.png}
    \end{minipage}%
    \begin{minipage}{0.05\textwidth}
    \hfill
    \end{minipage}
    \caption{Instantaneous flow structures observed at 40h in (a,c,e) 0.01$^{\circ}$ slope case and (b,d,f) 1$^{\circ}$ slope case. (a,b) Temperature in cross section mid-way through the y-axis. (c,d) Salinity in cross-section mid-way through the y-axis. (e,f) Cross-slope velocity fluctuations at 1 m below the ice-ocean interface. Note that the colorbar scale is smaller in (e) than (f).}
    % Add contours to a-d to show structures more clearly
    \label{fig:cross-section}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.4\textwidth}
        \includegraphics[trim={0 0cm 3cm 0cm},clip,width=\textwidth]{Figures/dslope2/e_hovmoller.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/e_hovmoller.png}
    \end{minipage}
    \caption{Example of turbulent intermittency as seen in white regions of turbulent kinetic energy (TKE). (a) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope. (b) An intermittent case: 0.45$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
    \label{fig:intermittency}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_dT_cmp_dT_43h_tav13h.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_slope_cmp_dslope_43h_tav13h.png}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0cm},clip,width=\textwidth]{Figures/gammaT_dT_cmp_dT_43h_tav13h.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0cm},clip,width=\textwidth]{Figures/gammaT_us_cmp_dslope_43h_tav13h.png}
    \end{minipage}
    \caption{(a) Melt rate vs. thermal driving. (b) Melt rate vs. slope. (c) Thermal exchange coefficient vs. far-field thermal driving for thermal driving simulations. Dashed line denotes the value recommended by \citeA{jenkins_observation_2010}. (d) Thermal exchange coefficient vs. friction velocity for sloped simulations. Note the difference in y-axis limits from (c). The 0.01$^{\circ}$ and 0.1$^{\circ}$ slope cases are overlapping.}
    \label{fig:melt_sensitivity}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_dTscale_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_slopescale_z_profile.png}
    \end{minipage}
    \caption{Vertical profile of heat flux averaged over the last inertial period for (a,c) temperature cases and (b,d) slope cases. (a,b) are in physical units while (c,d) are scaled by the Ekman depth, far-field thermal driving, and slope. The black curve is represents the same simulation in all panels. The horizontal axis limits vary between panels.} 
    %Consider replacing (d) with scaling by sin\alpha
    %Change scaled vertical axis limits to 0-40
    %Change all to centered on 43h and averaged 13h
    \label{fig:heatflux_profiles}
\end{figure}

@@

\begin{figure}[h!]
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_43h_tav13h_z_profile.png}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_43h_tav13h_z_profile.png}
    \end{minipage}
    \caption{Momentum flux averaged over the last inertial period for (a) thermal driving cases and (b) slope cases. Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid). Positive flux denotes upward flux (i.e., drag) and }
    \label{fig:momflux_profiles}
    % change x-axis labels to \overline{u_i'w'}
\end{figure}
